Title

### 2024-08-29 paper.tex
p comps

\subsection{The components of \texorpdfstring{\(\mathcal{P}\)}{P}}
\begin{corollary}
    They are just the components of the \(\mathcal{P}_{wr}\)'s.
\end{corollary}

>>>>

\subsection{The components of \texorpdfstring{\(\mathcal{P}\)}{P}}
\begin{corollary}
    Every irreducible components of \(\mathcal{P}\) is the closure of some subvariety of the form \(\varphi_{wr}(\mathcal{Q}_{w,r,I,(\rho_i),\alpha} \times G)\), and the closure of each subvariety of this form is an irreducible component.
    Each has dimension \(\sum_{ij} \min(\lambda_i, \lambda_j)\).
\end{corollary}
\begin{proof}
    Follows directly from \cref{pwr_comps}.
\end{proof}
